Classless Java: Tuning Java Interfaces

### 2015-11-25 paper/sections/Appendix.tex
Remove the feature of checking existence of ofMethod. Is buggy and nontrivial.

\subsection{Proof of LEMMA 1}\label{subsec:proof1}
\marco{this seams to be just a sublemma for Lemma2, I think you can mention it in the appendix only.}
\textbf{LEMMA 1. }
Assume that
\begin{align*}
\II_0\ &=\ \mixinAnn\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \cC\\
[\![\II_0]\!]\ &=\ \emptyset\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \methods' \cC
\end{align*}
If $\II_0$ satisfies $\dom(\C_0)=\dom(\C_1)\cup\ldots\cup\dom(\C_n)\cup\dom(\methods)$, then $[\![\II_0]\!]$ satisfies $\dom([\![\II_0]\!])=\dom(\C_1)\cup\ldots\cup\dom(\C_n)\cup\dom(\methods)\cup\dom(\methods')$.
\begin{proof}
It suffices to prove $\dom([\![\II_0]\!])=\dom(\C_0)\cup\dom(\methods')$.
\begin{itemize}
\item If $m\notin\dom(\methods')$, by the definition of $\mBody$, it is obtained from $\override$. The first argument of $\override$, namely $\methods\cup\methods'(m)$, is equal to $\methods(m)$, and the second argument is not changed as well, thus the result of $\override$ is not changed during translation. Hence $m\in\dom([\![\II_0]\!])$ iff $m\in\dom(\C_0)$.
\item If $m\in\dom(\methods')$, we are to prove $m\in\dom([\![\II_0]\!])$. So if $m$ is the $\QM{of}$ method generated by $\ofMethod$, its $\mBody$ value is well defined, by the rule $\override(\method,\none)=\method$.\marco{need to add here that we know of is not in dom(..)} On the other hand, if $m$ is generated by $\otherMethod$, namely $m$ is a $\QM{with-}$ or setter method,
 we can apply the last clause of override, since in the definition of $\otherMethod$, we can see $\isWith$ and $\isSetter$ ensure the compatible subtyping relationship. Hence $m\in\dom([\![\II_0]\!])$ as well.
\end{itemize}
\end{proof}

\marco{ we need to state (may be as a new lemma):
forall expressions e, if under interface table I0,I1..In
$\Gamma\vdash e\in\C$, then  under interface table [[I0]],I1..In
$\Gamma\vdash e\in\_<:\C$
ProofScatch:
(1) observing otherMethods(), we see that [I] is structurally a subtype of I, thus all the expressions typed in an interface table with I, are well typed in an interface table with [I]. 
The only interesting case is method call (normal, super and static)
consider $\Gamma\vdash e_0.m(e_1..e_n)\in\C$, with $e_0$ of type I0,
if it is well typed in the first table, then in the other table it is still well typed:
the method still exists and its argument types are the same type.
The expressions 1..n may be now typed in a subtype, but this is ok since the premise of the rule ask for $\_<:\C$
}
\subsection{Proof of LEMMA 2}\label{subsec:proof2}
\textbf{LEMMA 2. }
If $\II_0$ OK, then $[\![\II_0]\!]$ OK.
\begin{proof}

>>>>

\subsection{LEMMA 1 and Proof}\label{subsec:proof1}
\textbf{LEMMA 1. }
Assume that
\begin{align*}
\II_0\ &=\ \mixinAnn\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \cC\\
[\![\II_0]\!]\ &=\ \emptyset\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \methods' \cC
\end{align*}
If $\II_0$ satisfies $\dom(\C_0)=\dom(\C_1)\cup\ldots\cup\dom(\C_n)\cup\dom(\methods)$, then $[\![\II_0]\!]$ satisfies $\dom([\![\II_0]\!])=\dom(\C_1)\cup\ldots\cup\dom(\C_n)\cup\dom(\methods)\cup\dom(\methods')$.
\begin{proof}
It suffices to prove $\dom([\![\II_0]\!])=\dom(\C_0)\cup\dom(\methods')$.
\begin{itemize}
\item If $m\notin\dom(\methods')$, by the definition of $\mBody$, it is obtained from $\override$. The first argument of $\override$, namely $\methods\cup\methods'(m)$, is equal to $\methods(m)$, and the second argument is not changed as well, thus the result of $\override$ is not changed during translation. Hence $m\in\dom([\![\II_0]\!])$ iff $m\in\dom(\C_0)$.
\item If $m\in\dom(\methods')$, we are to prove $m\in\dom([\![\II_0]\!])$. So if $m$ is the $\QM{of}$ method generated by $\ofMethod$, its $\mBody$ value is well defined, by the rule $\override(\method,\none)=\method$.\marco{need to add here that we know of is not in dom(..)}\haoyuan{BTW, the condition of the translation should be $\QM{of}\notin\dom(\methods)$ or $\QM{of}\notin\dom(\C_0)$?} On the other hand, if $m$ is generated by $\otherMethod$, namely $m$ is a $\QM{with-}$ or setter method,
 we can apply the last clause of override, since in the definition of $\otherMethod$, we can see $\isWith$ and $\isSetter$ ensure the compatible subtyping relationship. Hence $m\in\dom([\![\II_0]\!])$ as well.
\end{itemize}
\end{proof}

\marco{ we need to state (may be as a new lemma):
forall expressions e, if under interface table I0,I1..In
$\Gamma\vdash e\in\C$, then  under interface table [[I0]],I1..In
$\Gamma\vdash e\in\_<:\C$
ProofScatch:
(1) observing otherMethods(), we see that [I] is structurally a subtype of I, thus all the expressions typed in an interface table with I, are well typed in an interface table with [I].
The only interesting case is method call (normal, super and static)
consider $\Gamma\vdash e_0.m(e_1..e_n)\in\C$, with $e_0$ of type I0,
if it is well typed in the first table, then in the other table it is still well typed:
the method still exists and its argument types are the same type.
The expressions 1..n may be now typed in a subtype, but this is ok since the premise of the rule ask for $\_<:\C$
}

\subsection{LEMMA 2 and Proof}\label{subsec:proofs}
\textbf{LEMMA 2. }
For any expression $e$ under an interface table $\II_0\ldots\II_n$ with $\Gamma\vdash e\in\C$, if $[\![\II_0]\!]$ is well-defined, then under the interface table $[\![\II_0]\!]\II_1\ldots\II_n$, $\Gamma\vdash e\in\_<:\C$.
\begin{proof}
The proof is based on induction. By the grammar shown in Figure~\ref{Grammar}, there are three cases for an arbitrary expression $e$:
\begin{itemize}
\item A variable or a field update. The type preservation for $e$ is ensured by induction.
\item A method call (normal, static or super). Such a method won't be ``removed'' by the translation and is still there, and the types of arguments remain unchanged. The only difference is that the return type can be refined, in which case the expression $e$ is typed in a subtype of $I$.?
\item An object creation.
\end{itemize}
\end{proof}

\subsection{Proof of LEMMA 2}\label{subsec:proof2}
\textbf{LEMMA 2. }
If $\II_0$ OK, then $[\![\II_0]\!]$ OK.
\begin{proof}

### 2015-11-25 paper/sections/Translation.tex
Remove the feature of checking existence of ofMethod. Is buggy and nontrivial.

\marco{ insert somewhere description of  fluent setter~\cite{the lombock thread, something about fluent stuff}.
This allows for convenient and chains of setters, as we will show later \marco{insert forward reference when available}}.

\subsection{Results}
\textbf{THEOREM. }
For a given $\II_0\ldots\II_n$ interface table such that
$\forall\II\in\II_0\ldots\II_n, \II$ OK,\\*
if  
$\valid(\C_0)$  and $\QM{of}\notin\dom(\C_0)$,
then in the interface table
$[\![\II_0]\!]\II_1\ldots\II_n$\\*
$\forall\II\in[\![\II_0]\!]\II_1\ldots\II_n$ either $\II$ OK or $\II$ is a subtype of $\II_0$.

\haoyuan{In theorem: $\C_0$ is valid and $\QM{of}\notin\dom(\C_0)$. To prove the theorem we need an extra lemma: if the translation is well defined, then $[\![\II_0]\!]$ is well formed.}

@@

\noindent\textbf{LEMMA 1. }
Assume that
\begin{align*}
\II_0\ &=\ \mixinAnn\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \cC\\
[\![\II_0]\!]\ &=\ \emptyset\ \QM{interface}\ \C_0\ \QM{extends}\ \Cs\ \oC \methods\ \methods' \cC
\end{align*}
If $\II_0$ satisfies $\dom(\C_0)=\dom(\C_1)\cup\ldots\cup\dom(\C_n)\cup\dom(\methods)$, then $[\![\II_0]\!]$ satisfies $\dom([\![\II_0]\!])=\dom(\C_1)\cup\ldots\cup\dom(\C_n)\cup\dom(\methods)\cup\dom(\methods')$.\\

>>>>

\marco{ insert somewhere description of  fluent setter~\cite{the-lombock-thread-something-about-fluent-stuff}.
This allows for convenient and chains of setters, as we will show later \marco{insert forward reference when available}}.

\subsection{Results}
\textbf{THEOREM. }
For a given $\II_0\ldots\II_n$ interface table such that
$\forall\II\in\II_0\ldots\II_n, \II$ OK,\\*
if $\II_0$ has \mixin,
$\valid(\C_0)$  and $\QM{of}\notin\dom(\C_0)$,
then in the interface table
$[\![\II_0]\!]\II_1\ldots\II_n$\\*
$\forall\II\in[\![\II_0]\!]\II_1\ldots\II_n$ either $\II$ OK or $\II$ is a subtype of $\II_0$.

@@
